---
Code for Master's Thesis: "Analyzing Technology Diffusion Pathways for the Deployment of Direct Air Capture in Meeting Global Climate Targets"

Author: "Tatjana Zurbriggen (modified Code-Version of Odenweller et al. (2022))"
---

# Setup
```{r setup, warning = FALSE}
options(repos = c(CRAN = "@CRAN@", pik = "https://rse.pik-potsdam.de/r/packages"))
install.packages("quitte")
install.packages("minpack.lm")
install.packages("openxlsx")

library(tidyverse)  # Data handling
library(quitte)  # Data handling
library(readxl)  # Reading excel files
library(ggplot2)  # Plotting
library(cowplot)  # Plotting layout
library(ggnewscale)  # Multiple legends
library(ggExtra)  # Marginal distributions
library(ggsci)  # Colour palettes
library(scales)  # Plotting axes
library(zoo)  # Function na.approx
library(ggforce)  # Function facet_zoom
library(colorspace)  # Colour manipulation40
library(minpack.lm) # Modelling
library(openxlsx) #Save as Excel
library(nleqslv)  # Solving non-linear systems of equations
library(truncnorm)  # Truncated normal distribution
library(lubridate)  # Working with dates
library(dbplyr) #Data handling

# Input data folder
path.input <- "01_input_data_new/"
# Output folder
path.output <- "02_output_plots_new/"
# Helper functions folder
path.helpers <- "03_helpers_new/"
# Plotting functions folder
path.plotting <- "04_plotting_new/"

# Source helper functions
source(paste0(path.helpers, "ReadDACProjectsDB.R"))
source(paste0(path.helpers, "ReadBPDB23.R"))
source(paste0(path.helpers, "calcTruncNormParam.R"))
source(paste0(path.helpers, "calcMonteCarloSample.R"))
source(paste0(path.helpers, "calcTechnologyDiffusion.R"))

# Source plotting functions
source(paste0(path.plotting, "plotDACProjects.R"))
source(paste0(path.plotting, "plotIllustration.R"))
source(paste0(path.plotting, "plotParameterDistributions.R"))
source(paste0(path.plotting, "plotProbabilisticFeasibilitySpace.R"))

#  Simulation mode: 
model.mode <- "simulation"

# Sample size
n <- 1000
# Minimum annual growth rate
bmin <- 0.15 #lower truncation of 15% per year

# For plotting
t.split <- 2025
t.min <- 2010
t.max <- 2050

# Set plotting style
font.size <- 6
theme_set(theme_cowplot(font_size = font.size))
color.pv <- "#ffb200"
color.wind <- "#215CAF"

# Quantile calculation. (i guess for extended data fig. 8)
quibble <- function(x, q = c(0.25, 0.33, 0.5, 0.66, 0.75)) {
  tibble(x = quantile(x, q), q = q)
}

# Regions
region.mapping.eu <- c(
  "Switzerland" = "Europe",
  "Iceland" = "Europe",
  "Norway" = "Europe",
  "Germany" = "Europe",
  "United Kingdom" = "Europe",
  "Netherlands" = "Europe",
  "Italy" = "Europe"
  
)
 region.mapping.northamerica <- c(
  "Canada" = "Canada",
  "United States" = "United States",
  "United States/Canada" = "United States/Canada"
)

region.mapping.global <- c(
  "Switzerland" = "Europe",
  "Iceland" = "Europe",
  "Norway" = "Europe",
  "Germany" = "Europe",
  "United Kingdom" = "Europe",
  "Netherlands" = "Europe",
  "Italy" = "Europe",
  "MENA" = "MENA",
  "Canada" = "North America",
  "United States" = "North America",
  "United States/Canada" = "North America",
  "South America" = "South America",
  "Australia" = "Australia",
  "Unspecified" = "Unspecified",
  "Other" = "Other"
  )
```

## Check file availability

```{r}
if (model.mode == "reproduction"){
  print("Model started in reproduction mode.")
  files.required <- c("02_output_plots_new/01_conventional_growth_parameters.rds",
                      "02_output_plots_new/02_conventional_growth_sample.rds",
                      "02_output_plots_new/03_conventional_growth_results.rds",
                    "02_output_plots_new/04_unconventional_growth_parameters.rds",
                      "02_output_plots_new/05_unconventional_growth_sample.rds",
                      "02_output_plots_new/06_unconventional_growth_results.rds")
  if (all(file.exists(files.required)) == TRUE){
    print("All required simulation result files found.")
  } else
    print("Required simulation result files are missing.")
} else if (model.mode == "simulation"){
  print("Model started in simulation mode.")
  } else {
  stop("Please specify either reproduction or simulation mode.")
}
```

# DAC Projects Database

```{r, message = FALSE}
# DAC Projects Database
file.dacprojects <- paste0(path.input, "Capacity DAC Projects Database 2023.xlsx")
data.dac <- ReadDACProjectsDB(
  file.dacprojects,
  dacprojects.range = "A5:N78",
  capacity.factor = 1.5
)
```


```{r, message = FALSE}
# Transformation Function
custom.trans <- function() {
  trans_new(name = 'custom', 
            transform = function(x) x^0.5,  #Transformation using the square roots
            inverse = function(x) x^2) #Inverse function for axis
}
```

## FIGURE 1: DAC Projects

```{r, message = FALSE}

regions.dac = tibble(name = c("Europe", "North America", "Global"),
  list = list(
    names(region.mapping.eu),
    names(region.mapping.northamerica),
    unique(data.dac$region)
    ))

# Europe
regions <- regions.dac$list[[1]]
names(regions) <- regions

p1 <- plotDACProjects(data.dac = data.dac,
                   regions = regions,
                   fill.by = "region",
                   title = "Europe: Country",
                   leg.label = "Country")

p2 <- plotDACProjects(data.dac = data.dac,
                   regions = regions,
                   title = "Europe: Status",
                   fill.by = "status",
                   leg.label = "Status")

# North America
regions <-  region.mapping.northamerica

p3 <- plotDACProjects(data.dac = data.dac,
                   regions = regions,
                   fill.by = "region",
                   title = "North America: Country",
                   leg.label = "Country")

p4 <- plotDACProjects(data.dac = data.dac,
                   regions = regions,
                   title = "North America: Status",
                   fill.by = "status",
                   leg.label = "Status")

# Global
regions <- region.mapping.global

p5 <- plotDACProjects(data.dac = data.dac,
                   regions = regions,
                   fill.by = "region",
                   title = "Global: Region",
                   leg.label = "Region")

p6 <- plotDACProjects(data.dac = data.dac,
                   regions = regions,
                   fill.by = "status",
                   title = "Global: Status",
                   leg.label = "Status")

p <- plot_grid(p1, p2, p3, p4, p5, p6,
               ncol = 2,
               labels = "auto",
               label_size = font.size)

print(p)
ggsave(paste0(path.output, "FIG01_dac_projects_without_SPB.png"),
       bg = "white", width = 20, height = 15, units = "cm")
ggsave(paste0(path.output, "FIG01_dac_projects_without_SPB.pdf"),
       bg = "white", width = 20, height = 15, units = "cm")

#write.xlsx(data.dac, file = "02_output_plots_new/data_results.xlsx")
```

# Case 1: Conventional Growth - Market Driven Case (Solar and Wind)

## Input data

### Wind and solar power capacities

```{r, message = FALSE}
# BP Statistical Review of World Energy 2023
file.bp <- paste0(path.input, "bp-stats-review-2023-all-data.xlsx")
data.bp <- ReadBPDB23(file.bp)
```

### DAC deployment targets

```{r}
data.targets <- tribble(
  ~ region, ~year, ~unit, ~value,
  
  #Europe Scenarios
  "Europe", 2025, "tCO2", 300000, #IPCC Ratio
  "Europe", 2030, "tCO2", 5000000, #EU Net Zero 
  "Europe", 2050, "tCO2", 152000000, #EU Net Zero 
  
  #North America Scenarios
  "North America", 2025, "tCO2", 1000000, #IEA Net Zero by 2050
  "North America", 2030, "tCO2", 38380000, #IPCC Ratio
  "North America", 2050, "tCO2", 549240000, #IPCC Ratio
  
  #Global Scenarios
  "Global", 2025, "tCO2", 14170000, #IPCC Ratio 
  "Global", 2030, "tCO2", 85000000, #IEA Net Zero Scenario 
  "Global", 2050, "tCO2", 980000000, #IEA Net Zero Scenario 
  )
 
```

## Emergence growth rate from wind and solar power

```{r, message = FALSE}

# Fit exponential growth of wind and solar power in slices of varying lengths

# Region mapping
regions.bp = tibble(name = c("Europe", "North America", "Global"),
                 list = list("Europe", "North America", "Global"),
                 span = list(1996:2010,
                             1996:2010,
                             1996:2010))

time.slice.length <- 5:10

# Additive error specification
exp_fit <- function(df) {
  nlsLM(capacity ~ a * (1 + b)^(year - 1996),
        data = df,
        start = list(a = 100, b = 0.4))
}


# Get growth rate
get_growthrate <- function(mod)
  coef(mod)[["b"]]

# Get parameter a
get_a <- function(mod)
  coef(mod)[["a"]]

# Get predicted values
get_predict <- function(mod)
  list(predict(mod))

# Loop over regions and time slices
data.bp.fit <- NULL
# Loop over regions
for (r in 1:dim(regions.bp)[1]) {
  time.span <- regions.bp$span[[r]]
  # Loop over lengths of time slice
  for (t in time.slice.length){
    # Get individual time slices for each length t
    for (s in 1:(length(time.span)-t+1)){
      slice <- time.span[s:(s+t-1)]
      
      temp <- data.bp %>% 
        filter(region %in% regions.bp$list[[r]],
               year %in% slice) %>% 
        group_by(technology, year) %>% 
        summarise(capacity = sum(capacity)) %>% 
        group_by(technology) %>% 
        nest() %>% 
        # Fit exponential models using purrr::map
        mutate(model.exp = map(data, exp_fit)) %>% 
        transmute(technology,
                  b = map_dbl(model.exp, get_growthrate),
                  a = map_dbl(model.exp, get_a),
                  predict = map(model.exp, get_predict),
                  slice.length = t,
                  slice.start = slice[1],
                  region = regions.bp$name[[r]])
     
      data.bp.fit <- bind_rows(data.bp.fit, temp)
    }
  }
}
```

## Monte Carlo sampling: Initial capacity, emergence growth rate

```{r, message = FALSE}

# Region mapping
if (model.mode == "simulation") {
  temp <- calcMonteCarloSample(
    # Sample size
    N = n,
    # Initial value distribution
    a.status = c("Decommissioned", "Operational", "Under Construction"),
    # Lower truncation = a 
    cap.1 = c("Decommissioned", "Operational", "Under Construction", "FID"),
    # Condition 1
    cumprob.1 = 0.15, # 15% Wahrscheinlichkeit für FID 
    # Cumulative probability of condition 1
    feasibilityAndDEP.success.rate = 0.3,
    # Condition 2: x % of feasibility study and design and engineering phase projects
    
    # Growth rate distribution (MAYBE I HAVE TO ADJUST IT!!!)
    slice.len = 10,
    # Length of time slice (wind, solar)
    b.min = bmin  # Lower truncation
  )
  data.input <- temp[[1]]
  data.input.param <- temp[[2]]
  saveRDS(data.input.param,
          "02_output_plots_new/01_conventional_growth_parameters.rds")
  saveRDS(data.input,
          "02_output_plots_new/02_conventional_growth_sample.rds")
} else if (model.mode == "reproduction") {
  data.input.param <-
    readRDS("02_output_plots_new/01_conventional_growth_parameters.rds")
  data.input <-
    readRDS("02_output_plots_new/02_conventional_growth_sample.rds")
}

```

## FIGURE 3: Parameter distributions

```{r, warning = FALSE}
plots <- plotParameterDistributions(data.input = data.input,
                                    data.input.param = data.input.param)

# Total plot
p.col1 <- plot_grid(plots[[1]] + theme(legend.position = "none"),
                    plots[[2]] + theme(legend.position = "none"),
                    NULL,
                    plots[[3]] + theme(legend.position = "none"),
                    ncol = 1,
                    align = "v",
                    rel_heights = c(1, 0.15, 0.05, 1.1),
                    labels = c("a", "", "","a"),
                    label_size = font.size
                    )

p.col2 <- plot_grid(plots[[4]] + theme(legend.position = "none"),
                    plots[[5]] + theme(legend.position = "none"),
                    NULL,
                    plots[[6]] + theme(legend.position = "none"),
                    ncol = 1,
                    align = "v",
                    rel_heights = c(1, 0.15, 0.05, 1.1),
                    labels = c("b", "", "","b"),
                    label_size = font.size
                    )

plots_global <- plotParameterDistributions(data.input = data.input, data.input.param)

plots <- c(plots, plots_global)

p.col3 <- plot_grid(plots[[7]] + theme(legend.position = "none"),
                    plots[[8]] + theme(legend.position = "none"),
                    NULL,
                    plots[[9]] + theme(legend.position = "none"),
                    ncol = 1,
                    align = "v",
                    rel_heights = c(1, 0.15, 0.05, 1.1),
                    labels = c("c", "", "","c"),
                    label_size = font.size
                    )

p.plots <- plot_grid(p.col1,
                     p.col2,
                     p.col3,
                     nrow = 1)

p.legend <- plot_grid(NULL,
                      get_legend(plots[[1]] + theme(legend.position = "bottom")),
                      get_legend(plots[[2]] + theme(legend.direction = "vertical")),
                      NULL,
                      nrow = 1,
                      rel_widths = c(1,0.9,0.7,1))

p <- plot_grid(p.plots,
               p.legend,
               ncol = 1,
               rel_heights = c(1,0.15))

print(p)
ggsave(paste0(path.output, "FIG03_parameter_distributions_without_SPB.png"),
       width = 18, height = 14, units = "cm", bg = "white")
ggsave(paste0(path.output, "FIG03_parameter_distributions_without_SPB.pdf"),
       width = 18, height = 14, units = "cm", bg = "white")



#write.xlsx(data.input, file = "02_output_plots_new/data_input.xlsx")
```

## Demand pull

```{r}
# Different anticipation scenarios (in years)
anticipation <- c(0, 5, 10, 100)  # 100y = full demand pull

# Model time span
model.time <- t.split:2050


data.demand <- NULL
for (r in 1:3){
  for (a in anticipation){
    
    # Targets in region
    targets.temp <- data.targets %>%
      filter(region == regions.dac$name[[r]])
    
    # Calculate linear demand pull with anticipation
    data.temp <- tibble(region = regions.bp$name[r],
                        year = model.time) %>%   
      mutate(demand = approx(x = targets.temp$year,
                             y = targets.temp$value,
                             xout = model.time ,    
                             method = "linear",
                             rule = 2)[["y"]]) %>% 
      mutate(demand = lead(demand, a, default = last(demand)),
             anticipation = a) %>% 
      group_by(region) %>%
      nest(demand = c("year", "demand")) %>% 
      ungroup()
    
    data.demand <- bind_rows(data.demand, data.temp)
  }
}
```

## Call simulation

```{r, message = F}
# Simulation mode
if (model.mode == "simulation") {
  # Keep track of time
  start.time <- Sys.time()
  # Call diffusion model
  data.results <-
    calcTechnologyDiffusion(data.demand, data.input, 0.25)
  # Save simulation results
  saveRDS(data.results,
          "02_output_plots_new/03_conventional_growth_results.rds")
  # Print duration of simulation
  end.time <- Sys.time()
  time.taken <- end.time - start.time
  print(time.taken)
  # Reproduction mode
} else if (model.mode == "reproduction") {
  data.results <-
    readRDS("02_output_plots_new/03_conventional_growth_results.rds")
}
```

## FIGURE 4: Probabilistic feasibility space

```{r}
#Definition of my own colors 

mycolors <- c("#A1AB71", "#66AFC0", "#7A9DCF") #ETH Green, Petrol and Blue 

colours <- mycolors

#colours <- pal_npg()(2)

p1 <- plotProbabilisticFeasibilitySpace(
  data.row = data.results %>%
    filter(region == "Europe", anticipation == 5),
  data.targets = data.targets,
  colour = colours[1],
  marginal.year = 2043,
  title = "Europe, +50% Capacity"
)

p2 <- plotProbabilisticFeasibilitySpace(
  data.row = data.results %>%
    filter(region == "North America", anticipation == 5),
  data.targets = data.targets,
  colour = colours[1],
  marginal.year = 2043,
  title = "North America, +50% Capacity"
)

p3 <- plotProbabilisticFeasibilitySpace(
  data.row = data.results %>%
    filter(region == "Global", anticipation == 5),
  data.targets = data.targets,
  colour = colours[1],
  marginal.year = 2043,
  title = "Global, +50% Capacity"
)

p.legend <- p3[[2]]

p.plots <- plot_grid(p1[[1]], p2[[1]],p3[[1]],
                     ncol = 3,
                     rel_widths = c(1, 1, 1, 1),
                     labels = c("m", "n", "o"),
                     label_size = font.size)

p <- plot_grid(p.plots,
               NULL,
               p.legend,
               ncol = 3,
               rel_widths = c(1, 0.05, 0.25, 0.025))


print(p)
ggsave(paste0(path.output, "FIG04_Probabilistic_Feasibility_Space_Conventional_+50.png"),
       width = 18, height = 5, units = "cm", bg = "white")
ggsave(paste0(path.output, "FIG04_Probabilistic_Feasibility_Space_Conventional_+50.pdf"),
       width = 18, height = 5, units = "cm", bg = "white")
```

## Quantiles of results

```{r, message = FALSE}
for (r in c("Europe", "North America", "Global")){
  
  stats <- data.results %>% 
  filter(region == r,
         anticipation == 5) %>% 
  select(!demand) %>% 
  unnest(sensitivities) %>% 
  unnest(results) %>% 
  filter(year %in% c(2025, 2030, 2050)) %>% 
  group_by(year) %>% 
  summarise(quibble(forecast))
  
  print(stats)
}
```


# Case 2: Unconventional Growth - Extrem Case (Several different Technologies)

## Input data

### WW2 US aircraft

```{r}
#www.aia-aerospace.org/wp-content/uploads/2016/06/Aviation-Facts-and-Figures-1945.pdf

data.ww2aircraft <- tibble(
  year = 1935:1944,
  prod = c(459, 1141, 949, 1800, 2141, 6086, 19290, 47873, 85946, 96369)
) %>% 
  mutate(value = cumsum(prod),
         unit = "units",
         tech = "WW2 US aircraft") %>% 
  select(!prod) %>% 
  mutate(number = 1)

```

### WW2 US liberty ships

```{r}
file.libertyships <- paste0(path.input, "Liberty_ships.xlsx")

data.libertyships <- read_excel(file.libertyships, sheet = "matlab") %>% 
  select(year, LS_cum) %>% 
  rename(value = LS_cum) %>% 
  group_by(year) %>% 
  slice(n()) %>% 
  mutate(unit = "units",
         tech = "WW2 US liberty ships") %>%
  ungroup() %>% 
  add_row(tibble(year = 1938,
                 unit = "units",
                 tech = "WW2 US liberty ships",
                 value = 0)) %>%
  arrange(year) %>% 
  mutate(number = 2)
```

### US nuclear weapons

```{r}
#https://doi.org/10.2968%2F066004008

file.nuclearweapons <- paste0(path.input, "Nuclear_weapons.xlsx")

data.usnuclearweapons <- read_excel(file.nuclearweapons, range = "A1:B57") %>% 
  rename(year = Year,
         value = US) %>% 
  mutate(unit = "units",
         tech = "US Nuclear weapons") %>% 
  filter(year <= 1967) %>% 
  mutate(number = 3)
```

### Soviet nuclear weapons

```{r}
#https://doi.org/10.2968%2F066004008

data.sovietnuclearweapons <-
  read_excel(file.nuclearweapons, range = "A1:C57") %>%
  rename(year = Year,
         value = Russia) %>% 
  select(!US) %>% 
  mutate(unit = "units",
         tech = "Soviet Nuclear weapons") %>% 
  filter(!is.na(value), year <= 1986) %>% 
  mutate(number = 4)
```

### Nuclear power in France

```{r, warning = FALSE}
data.nuclear <-
  read_excel(file.bp,
             sheet = "Nuclear Generation - TWh",
             range = "B3:BE32",
             col_types = "numeric") %>%
  slice(n()) %>% 
  pivot_longer(cols = "1965":"2020", names_to = "year", values_to = "value") %>% 
  mutate(year = as.integer(year),
         value = as.double(value),
         unit = "TWh/yr",
         tech = "Nuclear France") %>% 
  filter(year <= 2005) %>% 
  mutate(number = 5)
```

### Internet host count

```{r}
file.internet <- paste0(path.input, "Internet_host_count.xlsx")

data.internet <- read_excel(file.internet) %>% 
  mutate(year = decimal_date(date),
         value = value/1E6,
         unit = "million hosts",
         tech = "Internet host count") %>% 
  select(year, value, unit, tech) %>% 
  arrange(year) %>% 
  filter(year < 2018) %>% 
  mutate(number = 6)
```

### China high-speed rail network

```{r}
#https://uic.org/passenger/highspeed/article/high-speed-database-maps

file.chinahsr <- paste0(path.input, "china_hsr.xlsx")

data.chinahsr <- read_excel(file.chinahsr, sheet = "values") %>% 
  group_by(year) %>% 
  summarise(new = sum(km)) %>% 
  mutate(value = cumsum(new),
         unit = "km",
         tech = "High-speed rail China") %>% 
  select(year, value, unit, tech) %>% 
  complete(year = seq(2003, 2020)) %>% 
  fill(value, unit, tech) %>% 
  add_row(tibble(year = 2002,
                 value = 0,
                 unit = "km",
                 tech = "High-speed rail China")) %>% 
  arrange(year) %>% 
  mutate(number = 7)
```

### US dry shale gas

```{r}
#https://www.eia.gov/dnav/ng/hist/res_epg0_r5302_nus_bcfa.htm

file.shale <- paste0(path.input, "RES_EPG0_R5302_NUS_BCFa.xls")

data.shale <- read_excel(file.shale,
                         sheet = "Data 1",
                         range = "A4:B16",
                         col_names = c("date", "value")) %>% 
  mutate(unit = "billion cubic feet",
         tech = "US shale gas",
         year = decimal_date(date)) %>% 
  select(year, value, unit, tech) %>% 
  mutate(number = 8)
```

### Smartphone shipments (cumulative)

```{r}
#https://www.statista.com/statistics/263441/global-smartphone-shipments-forecast/
#https://www.statista.com/statistics/271539/worldwide-shipments-of-leading-smartphone-vendors-since-2007/
#https://www.researchgate.net/publication/50836092_Structuring_the_Smartphone_Industry_Is_the_Mobile_Internet_OS_Platform_the_Key/figures

data.smartphones <- tibble(
  year = 2006:2020,
  prod = c(64.1, 122.36, 151.4, 173.5, 304.7, 494.5, 725.3, 1018.7, 1301.7, 1437.2, 1473.4, 1465.5, 1402.6, 1371.1, 1280)
) %>% 
  mutate(value = cumsum(prod),
         unit = "million units",
         tech = "Smartphones globally") %>% 
  select(!prod) %>% 
  mutate(number = 9)
```

### Europe e-bike sales (cumulative)

```{r}
#https://www.statista.com/statistics/276036/unit-sales-e-bikes-europe/
#https://www.ziv-zweirad.de/fileadmin/redakteure/Downloads/Marktdaten/PM_2021_10.03._ZIV-Praesentation_10.03.2021_mit_Text.pdf

data.ebikes <- tibble(
  year = 2009:2020,
  sales = c(0.5, 0.7, 0.9, 1.1, 1, 1.25, 1.5, 1.74, 2.2, 2.92, 3.6, 5.1)
) %>% 
  mutate(value = cumsum(sales),
         unit = "million units",
         tech = "E-Bikes Europe") %>% 
  select(!sales) %>% 
  mutate(number = 10)
```

## Join datasets

```{r}
data.unconventional <- bind_rows(
  data.ww2aircraft,
  data.libertyships,
  data.usnuclearweapons,
  data.sovietnuclearweapons,
  data.nuclear,
  data.internet,
  data.chinahsr,
  data.shale,
  data.smartphones,
  data.ebikes
) %>% 
  group_by(tech) %>% 
  mutate(value.norm = value/max(value)) %>%
  ungroup() %>% 
  arrange(number, year)
```

## Estimate logistic growth rates

```{r}
# Loop over technologies and time slices
param.unconventional.fit <- NULL
techs <- data.unconventional %>% 
  pull(tech) %>% 
  unique()
for (i in techs) {
  # Filter technology
  data.tech <- data.unconventional %>%
    filter(tech == i)
  fit <- nls(value.norm ~ SSlogis(year, Asym, xmid, scal),
             data = data.tech)
  r <- exp(1/coef(fit)["scal"]) - 1  # Transform into annual growth rate
  # Temporary data to save
  temp <- tibble(
    tech = i,
    b = r
  )
  param.unconventional.fit <- bind_rows(param.unconventional.fit, temp)
}
```

## Re-parameterise growth distribution

```{r}
if (model.mode == "simulation"){
# New growth rate distribution
b.mean <- mean(param.unconventional.fit %>% pull(b))
b.sd <- sd(param.unconventional.fit %>% pull(b))
# New growth rate sample
b.sample <- rtruncnorm(n = n, a = 0.15, b = Inf, mean = b.mean, sd = b.sd)
data.input.unconv <- data.input
data.input.unconv$growth <- rep(b.sample, 3)  # For Europe, North America and Global
# New input file
data.input.param.unconv <- data.input.param %>% 
  select(!c(growth.solar, growth.wind))
# New growth parameter values
data.input.param.unconv$growth.min <- bmin
data.input.param.unconv$growth.mean <- b.mean
data.input.param.unconv$growth.sd <- b.sd
data.input.param.unconv$growth.sample.mean <- mean(b.sample)
data.input.param.unconv$growth.sample.sd <- sd(b.sample)
data.input.param.unconv$growth.sample.q25 <- quantile(b.sample, 0.25)
data.input.param.unconv$growth.sample.q75 <- quantile(b.sample, 0.75)
# Save parameters and sample
saveRDS(data.input.param.unconv, "02_output_plots_new/04_unconventional_growth_parameters.rds")
saveRDS(data.input.unconv, "02_output_plots_new/05_unconventional_growth_sample.rds")
} else if (model.mode == "reproduction"){
  # Load parameters and sample
  data.input.param.unconv <- readRDS("02_output_plots_new/04_unconventional_growth_parameters.rds")
  data.input.unconv <- readRDS("02_output_plots_new/05_unconventional_growth_sample.rds")
}
```

## Call simulation

```{r}
if (model.mode == "simulation") {
  # Keep track of time
  start.time <- Sys.time()
  # Call diffusion model
  data.results.unconv <-
    calcTechnologyDiffusion(data.demand, data.input.unconv, 0.25)
  # Save simulation results
  saveRDS(data.results.unconv,
          "02_output_plots_new/06_unconventional_growth_results.rds")
  # Print duration of simulation
  end.time <- Sys.time()
  time.taken <- end.time - start.time
  print(time.taken)
  
} else if (model.mode == "reproduction") {
  data.results.unconv <-
    readRDS("02_output_plots_new/06_unconventional_growth_results.rds")
}
```

## FIGURE 5: Unconventional growth

```{r, warning = FALSE}
techs <- data.unconventional %>% 
  pull(tech) %>% 
  unique()
colors.tech <- pal_lancet()(length(techs))
names(colors.tech) <- techs

top <- 1.1
mid <- 0.9
low <- 0.7

# Annotation labels
data.plot.labels <- tribble(
  ~year, ~ypos, ~color, ~label,
  1938, top, "WW2 US aircraft", "1: WWII US\naircraft",
  1946, mid, "WW2 US liberty ships", "2: WWII US\nliberty ships",
  1960, top, "US Nuclear weapons", "3: US nuclear\nweapons",
  1966, mid, "Soviet Nuclear weapons", "4: Soviet nuclear\nweapons",
  1986, top, "Nuclear France", "5: Nuclear power\nFrance",
  1998, low, "Internet host count", "6: Internet\nhosts",
  2005, top, "High-speed rail China", "7: High-speed\nrail China",
  2020, top, "US shale gas", "8: US dry\nshale gas",
  2020, low, "Smartphones globally", "9: Smartphones\nglobally",
  2021, 0.5, "E-Bikes Europe", "10: E-Bikes\nEurope"
)

# PANEL a: Unconventional growth curves
p.curves <- ggplot() +
  geom_line(data = data.unconventional,
            mapping = aes(x = year, y = value.norm, color = tech)) + 
  scale_color_manual(name = NULL,
                     values = colors.tech) +
  scale_x_continuous(name = "Year",
                     breaks = seq(1940, 2020, 10),
                     limits = c(1938, 2032)) +
  scale_y_continuous(name = "Deployment Levels (relative to maximum)") + 
  ggtitle("Normalised Unconventional Growth") +
  theme(axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        plot.title = element_text(
            face = "bold",
            size = font.size)) +
  geom_label(data = data.plot.labels,
            mapping = aes(x = year, y = ypos, label = label, color = color),
            size = 5 / .pt,
            fontface = "bold",
            hjust = 0,
            label.padding = unit(0.7, "mm")) +
  coord_cartesian(ylim = c(0, 1.2),clip = "off") +
  geom_line(mapping = aes(x = c(1938, 2024), y = 1),
            linetype = "dotted",
            alpha = 0.5)

growth.min <- 0.15
growth.max <- 4

# Sample
data.plot.sample <- data.input.unconv %>% 
  filter(region == "Global")  # The same anyway

# Density
data.plot.density <- tibble(
  growth = seq(growth.min, growth.max, length.out = 100),
  growth.dens = dtruncnorm(growth,
                           a = growth.min,
                           mean = data.input.param.unconv$growth.mean[[1]],
                           sd = data.input.param.unconv$growth.sd[[1]])
)

data.plot.growthrates <- param.unconventional.fit %>% 
  ungroup() %>% 
  mutate(number = 1:n()) %>% 
  arrange(b) %>% 
  mutate(order = 1:n()) %>% 
  mutate(ypos = case_when(order %% 4 == 1 ~ 0.45,
                          order %% 4 == 2 ~ 0.35,
                          order %% 4 == 3 ~ 0.25,
                          order %% 4 == 0 ~ 0.15))

bins <- 20

# PANEL b: Growth rates
p.growth <- ggplot() + 
  # Sample
  geom_histogram(data = data.plot.sample,
                 mapping = aes(x = 100*growth, y = 100*..density.., color = "Sample"),
                 binwidth = (100*growth.max - 100*growth.min)/bins,
                 boundary = 100*growth.min,
                 alpha = 0.3) +
  scale_color_manual(name = NULL, values = c("Sample" = "#E2E2E2")) +
  # Distribution
  new_scale_color() +
  geom_line(data = data.plot.density,
            mapping = aes(x = 100*growth, y = growth.dens, color = "Density")) +
  scale_color_manual(name = NULL, values = c("Density" = "black")) +
  new_scale_color() + 
  # Vertical lines
  geom_vline(data = data.plot.growthrates,
             mapping = aes(xintercept = 100*b,
                           color = tech),
             linetype = "dotted") + 
  scale_color_manual(name = NULL,
                     values = colors.tech) +
  # Numbers in boxes
  geom_label(data = data.plot.growthrates,
             mapping = aes(x = b*100,
                           y = ypos,
                           label = number,
                           color =  tech),
             size = 6 /.pt,
             label.padding = unit(0.7, "mm")) +
  scale_x_continuous(name = "Emergence Growth Rate [%/yr]",
                     limits = c(0, 100*growth.max)) + 
  ylab("Probability Density [yr]") +
  ggtitle("Distribution of Unconventional Growth Rates") +
  theme(axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        plot.title = element_text(
          face = "bold",
          size = font.size))
# Arrange plots
p.row1 <- plot_grid(p.curves + theme(legend.position = "none"),
                    p.growth + theme(legend.position = "none"),
                    ncol = 2,
                    rel_widths = c(0.6, 0.4),
                    labels = c("d", "e"),
                    label_size = font.size)

p <- plot_grid(p.row1,
               NULL,
               ncol = 1,
               rel_heights = c(1, 0.05, 1))

print(p)
ggsave(paste0(path.output, "FIG05_PFS_Unconventional_Standard_Rates_without_SPB.png"),
       width = 18, height = 6, units = "cm", bg = "white")
ggsave(paste0(path.output, "FIG05_PFS_Unconventional_Standard_Rates_without_SPB.pdf"),
       width = 18, height = 6, units = "cm", bg = "white")
```


```{r, warning = FALSE}
# PANEL c + d + e: Unconventional DAC growth
#Definition of my own colors 

mycolors <- c("#A1AB71", "#66AFC0", "#7A9DCF") #ETH Green, Petrol and Blue 

colours <- mycolors

p1 <-
  plotProbabilisticFeasibilitySpace(
    data.row = data.results.unconv %>%
      filter(region == "Europe", anticipation == 5),
    data.targets = data.targets,
    colour = colours[2],
    marginal.year = 2032,
    title = "Europe, +50% Capacity",
    ci.80 = T,
    zoom = F
  )

p2 <-
  plotProbabilisticFeasibilitySpace(
    data.row = data.results.unconv %>%
      filter(region == "North America", anticipation == 5),
    data.targets = data.targets,
    colour = colours[2],
    marginal.year = 2032,
    title = "North America, +50% Capacity",
    ci.80 = T,
    zoom = F
  )

p3 <-
  plotProbabilisticFeasibilitySpace(
    data.row = data.results.unconv %>%
      filter(region == "Global", anticipation == 5),
    data.targets = data.targets,
    colour = colours[2],
    marginal.year = 2032,
    title = "Global, +50% Capacity",
    ci.80 = T,
    zoom = F
  )

# Arrange plots
p.row2 <- plot_grid(p1[[1]],
                    NULL,
                    p2[[1]],
                    NULL,
                    p3[[1]],
                    NULL,
                    p3[[2]],
                    ncol = 8,
                    rel_widths = c(1, 0.025, 1, 0.025, 1, 0.025),
                    labels = c("m", "", "n", "","o", ""),
                    label_size = font.size)

p <- plot_grid(p.row2,
               ncol = 1,
               rel_heights = c(1, 0.05, 0.025))

print(p)
ggsave(paste0(path.output, "FIG05_PFS_Unconventional_Standard_+50.png"),
       width = 18, height = 5, units = "cm", bg = "white")
ggsave(paste0(path.output, "FIG05_PFS_Unconventional_Standard_+50.pdf"),
       width = 18, height = 5, units = "cm", bg = "white")
```

# Case 3: Conservative Growth - Less Ambitious Case (Similar Technologies)

## Input data

### CCS (Installed Capacity World) 

```{r}

data.ccs <- tibble(
  year = 1971:2019,
  sales = c(0.5,	0.5,	0.5,	0.5,	0.5,	0.5,	0.5,	0.5,	0.5,	0.5,	0.5,	1.2,	1.2,	1.2,	1.2,	8.2,	8.2,	8.2,	8.2,	8.2,	8.2,	8.2,	8.2,	8.2,	8.2,	9.2,	9.2,	9.2,	9.2,	12.2,	12.2,	12.2,	12.2,	12.2,	12.2,	12.2,	12.2,	12.9,	12.9,	21.3,	21.3,	21.3,	27.2,	28.2,	30,	30.8,	33.2,	33.8,	37.5)
) %>% 
  mutate(value = cumsum(sales),
         unit = "GW",
         tech = "CCS Global Installed Capacity") %>% 
  select(!sales) %>% 
  mutate(number = 3)
```


### Municipal Waste Materials Recycled in EU

```{r}

data.mswrecylcled <- tibble(
  year = 1995:2021,
  sales = c(23, 26, 30, 32, 37, 38, 40, 43, 43, 43, 46, 47, 52, 53, 54, 55, 56, 58, 56, 59, 63, 65, 65, 66, 67, 69, 70)
) %>% 
  mutate(value = cumsum(sales),
        unit = "Million Metric Tons",
         tech = "Total Municipal Waste Materials Recycled in EU") %>% 
  select(!sales) %>% 
  mutate(number = 4)
```

### Global Ammonia Synthesis Production

```{r}

data.ammonia <- tibble(
  year = 1924:2020,
  sales = c(255, 289, 300, 367, 2598, 2645.6, 2133.4, 2107.4, 2236.9, 2327, 2603, 3023, 3385, 3645, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 3589.987, 3956.773, 4462.385, 4808.62, 5540, 6300, 6650, 7280, 8530, 9390, 9780, 10740, 12937.059, 13544.151, 15477.434, 17609.862, 20325.168, 23070.228, 25836.183, 28141.97, 30195.308, 33258.266, 35249.174, 38350.337, 41033.282, 42414.805, 44619.593, 46449.524, 50468.029, 55909.463, 59622.703, 62777.606, 62291.849, 63493.886, 68268.923, 74855.695, 73680.818, 77696.274, 82028.36, 85767.301, 85185.849, 82279.841, 80831.186, 80314.695, 80302.72, 80011.675, 86486.98, 90418.464, 87566.043, 88392.236, 89161.871, 85129.097, 85670.741, 87334.65659, 88722.23565, 94211.27627, 95401.6224, 95157.92192, 102402.8279, 100266.5045, 98588.04969, 107431.9324, 107783.99, 109821.5327, 114908.875, 115823.0681, 120785.4006, 119405.796, 120677.587, 121230.526, 123987.3633, 123145.0518)
) %>% 
  mutate(value = cumsum(sales),
         unit = "Thousand Metric Tons of Nitrogen Equivalent",
         tech = "Global Annual Ammonia Synthesis Production") %>% 
 select(!sales) %>% 
  mutate(number = 1)
```

### Global Nuclear Energy Production

```{r}

data.nuclear <- tibble(
  year = 1965:2021,
  sales = c(25.53972424,	34.43329033,	41.006014,	52.11316407,	61.78341156,	78.87465713,	109.7041774,	152.1751488,	203.9015793,	266.6000934,	369.8481907,	432.671421,	538.5478136,	625.794396,	650.8598947,	711.924223,	840.7507617,	912.1775425,	1033.81271,	1254.568438,	1488.921637,	1594.735734,	1734.733117,	1891.249267,	1945.010586,	2000.462024,	2096.174705,	2112.089141,	2184.826061,	2225.844324,	2322.395978,	2406.801052,	2390.276558,	2431.421909,	2523.952702,	2580.899081,	2653.767774,	2696.170555,	2641.568435,	2761.605227,	2768.867742,	2803.365936,	2746.229909,	2737.70771,	2698.983475,	2768.505889,	2652.676552,	2470.77955,	2490.533299,	2541.382685,	2575.592424,	2613.905875,	2637.234693,	2700.464015,	2796.354063,	2693.978613,	2800.267792)
) %>% 
  mutate(value = cumsum(sales),
         unit = "TWh",
         tech = "Global Annual Nuclear Energy Production") %>% 
  select(!sales) %>% 
  mutate(number = 2)
```

### Liquefied Natural Gas Production in US

```{r}

data.naturalgas <- tibble(
  year = 1985:2021,
  sales = c(52.88,	50.17,	48.6,	51.57,	51.42,	52.55,	54.01,	52.53,	55.99,	62.68,	65.28,	67.65,	62.19,	65.98,	63.88,	66.03,	66.22,	63.84,	66.08,	62.47,	65.37,	60.94,	48.49,	39.22,	33.36,	64.79,	70,	28.3,	2.92,	16.26,	28.38,	186.84,	707.54,	1083.12,	1819.4,	2389.84,	3560.82)
) %>% 
  mutate(value = cumsum(sales),
         unit = "Billion Cubic Feet",
         tech = "Annual Production Liquefied Natural Gas in US") %>% 
  select(!sales) %>% 
  mutate(number = 5)
```

## Join datasets Conservative Growth

```{r}
data.conservative <- bind_rows( 
 data.ccs,
 data.mswrecylcled,
data.ammonia,
data.nuclear,
data.naturalgas
) %>% 
  group_by(tech) %>% 
  mutate(value.norm = value/max(value)) %>%
  ungroup() %>% 
  arrange(number, year)
```

## Estimate logistic growth rates Conservative Growth

```{r}
# Loop over technologies and time slices
param.conservative.fit <- NULL
techs <- data.conservative %>%
  pull(tech) %>% 
  unique()

for (i in techs) {
  # Filter technology
  data.tech <- data.conservative %>%
    filter(tech == i)
  
  # Provide initial parameter values
  start_values <- c(Asym = max(data.tech$value.norm), xmid = median(data.tech$year), scal = 1)
  
  # Fit logistic growth model using nlsLM from minpack.lm
  fit <- nlsLM(value.norm ~ SSlogis(year, Asym, xmid, scal),
               data = data.tech,
               start = start_values,
               control = nls.lm.control(maxiter = 1000))  # Increase the maximum number of iterations
  
  r <- exp(1/coef(fit)["scal"]) - 1  # Transform into annual growth rate
  
  # Temporary data to save
  temp <- tibble(
    tech = i,
    b = r
  )
  param.conservative.fit <- bind_rows(param.conservative.fit, temp)
}

```

## Re-parameterise growth distribution Conservative Growth

```{r}
if (model.mode == "simulation"){
# New growth rate distribution
b.mean <- mean(param.conservative.fit %>% pull(b))
b.sd <- sd(param.conservative.fit %>% pull(b))
# New growth rate sample
b.sample <- rtruncnorm(n = n, a = 0.08, b = Inf, mean = b.mean, sd = b.sd)
data.input.conserv <- data.input
data.input.conserv$growth <- rep(b.sample, 3)  # For Europe, North America and Global
# New input file
data.input.param.conserv <- data.input.param %>% 
  select(!c(growth.solar, growth.wind))
# New growth parameter values
data.input.param.conserv$growth.min <- bmin
data.input.param.conserv$growth.mean <- b.mean
data.input.param.conserv$growth.sd <- b.sd
data.input.param.conserv$growth.sample.mean <- mean(b.sample)
data.input.param.conserv$growth.sample.sd <- sd(b.sample)
data.input.param.conserv$growth.sample.q25 <- quantile(b.sample, 0.25)
data.input.param.conserv$growth.sample.q75 <- quantile(b.sample, 0.75)
# Save parameters and sample
saveRDS(data.input.param.conserv, "02_output_plots_new/04_unconventional_growth_parameters.rds")
saveRDS(data.input.conserv, "02_output_plots_new/05_unconventional_growth_sample.rds")
} else if (model.mode == "reproduction"){
  # Load parameters and sample
  data.input.param.conserv <- readRDS("02_output_plots_new/04_unconventional_growth_parameters.rds")
  data.input.conserv <- readRDS("02_output_plots_new/05_unconventional_growth_sample.rds")
}
#write.xlsx(data.input.conserv, file = "02_output_plots_new/data_input_conserv.xlsx")
```

## Call simulation Conservative Growth

```{r}
if (model.mode == "simulation") {
  # Keep track of time
  start.time <- Sys.time()
  # Call diffusion model
  data.results.conserv <-
    calcTechnologyDiffusion(data.demand, data.input.conserv, 0.25)
  # Save simulation results
  saveRDS(data.results.conserv,
          "02_output_plots_new/07_conservative_growth_results.rds")
  # Print duration of simulation
  end.time <- Sys.time()
  time.taken <- end.time - start.time
  print(time.taken)
  
} else if (model.mode == "reproduction") {
  data.results.conserv <-
    readRDS("02_output_plots_new/07_conservative_growth_results.rds")
}
```

## FIGURE 6: Conservative Growth

```{r, warning = FALSE}
techs <- data.conservative %>% 
  pull(tech) %>% 
  unique()
colors.tech <- pal_npg()(length(techs))
names(colors.tech) <- techs

top <- 1.1
mid <- 0.9
low <- 0.7

# Annotation labels
data.plot.labels <- tribble(
  ~year, ~ypos, ~color, ~label,
  1985, top, "CCS Global Installed Capacity", "3: CCS\nGlobal Capacity",
  2000, top, "Total Municipal Waste Materials Recycled in EU", "4: MSW\nRecycled EU",
  1950, top, "Global Annual Ammonia Synthesis Production", "1: Global Ammonia\nSynthesis Production",
  1970, top, "Global Annual Nuclear Energy Production", "2: Global Nuclear\nEnergy Production",
 2015, top, "Annual Production Liquefied Natural Gas in US", "5: US Natural\nGas Production"
)

# PANEL a: Conservative growth curves
p.curves <- ggplot() +
  geom_line(data = data.conservative,
            mapping = aes(x = year, y = value.norm, color = tech)) + 
  scale_color_manual(name = NULL,
                     values = colors.tech) +
  scale_x_continuous(name = "Year",
                     breaks = seq(1950, 2020, 10),
                     limits = c(1950, 2025)) +
  scale_y_continuous(name = "Deployment Levels (relative to maximum)") + 
  ggtitle("Normalised Conservative Growth") +
  theme(axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        plot.title = element_text(
            face = "bold",
            size = font.size)) +
  geom_label(data = data.plot.labels,
            mapping = aes(x = year, y = ypos, label = label, color = color),
            size = 5 / .pt,
            fontface = "bold",
            hjust = 0,
            label.padding = unit(0.7, "mm")) +
  coord_cartesian(ylim = c(0, 1.2),clip = "off") +
  geom_line(mapping = aes(x = c(1950, 2025), y = 1),
            linetype = "dotted",
            alpha = 0.5)

growth.min <- 0.08
growth.max <- 0.75


# Sample
data.plot.sample <- data.input.conserv %>% 
  filter(region == "Global")  # The same anyway

# Density
data.plot.density <- tibble(
  growth = seq(growth.min, growth.max, length.out = 100),
  growth.dens = dtruncnorm(growth,
                           a = growth.min,
                           mean = data.input.param.conserv$growth.mean[[1]],
                           sd = data.input.param.conserv$growth.sd[[1]])
)

data.plot.growthrates <- param.conservative.fit %>% 
  ungroup() %>% 
  mutate(number = 1:n()) %>% 
  arrange(b) %>% 
  mutate(order = 1:n()) %>% 
  mutate(ypos = case_when(order %% 5 == 1 ~ 2.5,
                          order %% 5 == 2 ~ 2,
                          order %% 5 == 3 ~ 1.5,
                          order %% 5 == 4 ~ 1,
                          order %% 5 == 0 ~ 0.5))

bins <- 20

# PANEL b: Growth rates
p.growth <- ggplot() + 
  # Sample
  geom_histogram(data = data.plot.sample,
                 mapping = aes(x = 100*growth, y = 100*..density.., color = "Sample"),
                 binwidth = (100*growth.max - 100*growth.min)/bins,
                 boundary = 100*growth.min,
                 alpha = 0.3) +
  scale_color_manual(name = NULL, values = c("Sample" = "#E2E2E2")) +
  # Distribution
  new_scale_color() +
  geom_line(data = data.plot.density,
            mapping = aes(x = 100*growth, y = growth.dens, color = "Density")) +
  scale_color_manual(name = NULL, values = c("Density" = "black")) +
  new_scale_color() + 
  # Vertical lines
  geom_vline(data = data.plot.growthrates,
             mapping = aes(xintercept = 100*b,
                           color = tech),
             linetype = "dotted") + 
  scale_color_manual(name = NULL,
                     values = colors.tech) +
  # Numbers in boxes
  geom_label(data = data.plot.growthrates,
             mapping = aes(x = b*100,
                           y = ypos,
                           label = number,
                           color =  tech),
             size = 6 /.pt,
             label.padding = unit(0.7, "mm")) +
  scale_x_continuous(name = "Emergence Growth Rate [%/yr]",
                     limits = c(0, 100*growth.max)) + 
  ylab("Probability density") +
  ggtitle("Distribution of Conservative Growth Rates") +
  theme(axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        plot.title = element_text(
          face = "bold",
          size = font.size))


# Arrange plots
p.row1 <- plot_grid(p.curves + theme(legend.position = "none"),
                    p.growth + theme(legend.position = "none"),
                    ncol = 2,
                    rel_widths = c(0.6, 0.4),
                    labels = c("f", "g"),
                    label_size = font.size)

p <- plot_grid(p.row1,
               NULL,
               ncol = 1,
               rel_heights = c(1, 0.05, 1))

print(p)
ggsave(paste0(path.output, "FIG06_PFS_Conservative_Standard_Rates_without_SPB.png"),
       width = 18, height = 6, units = "cm", bg = "white")
ggsave(paste0(path.output, "FIG06_PFS_Conservative_Standard_Rates_without_SPB.pdf"),
       width = 18, height = 6, units = "cm", bg = "white")
```




```{r, warning = FALSE}

# PANEL c + d: Conservative DAC growth

#Definition of my own colors 

mycolors <- c("#A1AB71", "#66AFC0", "#7A9DCF") #ETH Green, Petrol and Blue 

colours <- mycolors

p1 <-
  plotProbabilisticFeasibilitySpace(
    data.row = data.results.conserv %>%
      filter(region == "Europe", anticipation == 5),
    data.targets = data.targets,
    colour = colours[3],
    marginal.year = 2048,
    title = "Europe, +50% Capacity",
    ci.80 = T,
    zoom = F
  )

p2 <-
  plotProbabilisticFeasibilitySpace(
    data.row = data.results.conserv %>%
      filter(region == "North America", anticipation == 5),
    data.targets = data.targets,
    colour = colours[3],
    marginal.year = 2045,
    title = "North America, +50% Capacity",
    ci.80 = T,
    zoom = F
  )
p3 <-
  plotProbabilisticFeasibilitySpace(
    data.row = data.results.conserv %>%
      filter(region == "Global", anticipation == 5),
    data.targets = data.targets,
    colour = colours[3],
    marginal.year = 2047,
    title = "Global, +50% Capacity",
    ci.80 = T,
    zoom = F
  )

# Arrange plots
p.row2 <- plot_grid(p1[[1]],
                    NULL,
                    p2[[1]],
                    NULL,
                    p3[[1]],
                    NULL,
                    p3[[2]],
                    ncol = 8,
                    rel_widths = c(1, 0.025, 1, 0.025, 1, 0.025),
                    labels = c("m", "", "n", "","o", ""),
                    label_size = font.size)

p <- plot_grid(p.row2,
               ncol = 1,
               rel_heights = c(1, 0.05, 0.025))

print(p)
ggsave(paste0(path.output, "FIG06_PFS_Conservative_Standard_+50.png"),
       width = 18, height = 5, units = "cm", bg = "white")
ggsave(paste0(path.output, "FIG06_PFS_Conservative_Standard_+50.pdf"),
       width = 18, height = 5, units = "cm", bg = "white")
```



## FIGURE 7: Conventional growth sensitivity analysis of anticipation

```{r}
p1 <- plotProbabilisticFeasibilitySpace(
  data.row = data.results %>%
    filter(region == "Europe", anticipation == 0),
  data.targets = data.targets,
  colour = colours[1],
  marginal.year = 2038,
  title = "Europe, no anticipation",
  zoom.panel = F
)

p2 <- plotProbabilisticFeasibilitySpace(
  data.row = data.results %>%
    filter(region == "North America", anticipation == 0),
  data.targets = data.targets,
  colour = colours[1],
  marginal.year = 2038,
  title = "North America, no anticipation",
  zoom.panel = F
)

p3 <- plotProbabilisticFeasibilitySpace(
  data.row = data.results %>%
    filter(region == "Global", anticipation == 0),
  data.targets = data.targets,
  colour = colours[1],
  marginal.year = 2045,
  title = "Global, no anticipation",
  zoom.panel = F
)

p4 <- plotProbabilisticFeasibilitySpace(
  data.row = data.results %>%
    filter(region == "Europe", anticipation == 10),
  data.targets = data.targets,
  colour = colours[1],
  marginal.year = 2038,
  title = "Europe, 10 years anticipation",
 zoom.panel = F
)

p5 <- plotProbabilisticFeasibilitySpace(
  data.row = data.results %>%
    filter(region == "North America", anticipation == 10),
  data.targets = data.targets,
  colour = colours[1],
  marginal.year = 2038,
  title = "North America, 10 years anticipation",
  zoom.panel = F
)

p6 <- plotProbabilisticFeasibilitySpace(
  data.row = data.results %>%
    filter(region == "Global", anticipation == 10),
  data.targets = data.targets,
  colour = colours[1],
  marginal.year = 2045,
  title = "Global, 10 years anticipation",
  zoom.panel = F
)

p7 <- plotProbabilisticFeasibilitySpace(
  data.row = data.results %>%
    filter(region == "Europe", anticipation == 100),
  data.targets = data.targets,
  colour = colours[1],
  marginal.year = 2038,
  title = "Europe, full anticipation",
  zoom.panel = F
)

p8 <- plotProbabilisticFeasibilitySpace(
  data.row = data.results %>%
    filter(region == "North America", anticipation == 100),
  data.targets = data.targets,
  colour = colours[1],
  marginal.year = 2038,
  title = "North America, full anticipation",
  zoom.panel = F
)

p9 <- plotProbabilisticFeasibilitySpace(
  data.row = data.results %>%
    filter(region == "Global", anticipation == 100),
  data.targets = data.targets,
  colour = colours[1],
  marginal.year = 2045,
  title = "Global, full anticipation",
  zoom.panel = F
)

p.legend <- p1[[2]]

p.plots <- plot_grid(p1[[1]], p2[[1]],p3[[1]],
                     p4[[1]], p5[[1]],p6[[1]],
                     p7[[1]], p8[[1]],p9[[1]],
                     ncol = 3,
                     rel_widths = c(1, 1),
                     labels = "auto",
                     label_size = font.size)

p <- plot_grid(p.plots,
               NULL,
               p.legend,
               ncol = 3,
               rel_widths = c(1, 0.05, 0.15))

print(p)
ggsave(paste0(path.output, "FIG07_Sensitivity_Anticipation_Conventional_Pull_+50.jpg"),
       width = 18, height = 18, units = "cm", bg = "white")
```

## Quantiles of Sensitivity Results (anticipation = 5)

```{r, message = FALSE}
for (r in c("Europe", "North America", "Global")){
  
  stats <- data.results %>% 
  filter(region == r,
         anticipation == 5) %>% 
  select(!demand) %>% 
  unnest(sensitivities) %>% 
  unnest(results) %>% 
  filter(year %in% c(2025, 2030, 2050)) %>% 
  group_by(year) %>% 
  summarise(quibble(forecast))
  
  print(stats)
}
#write.xlsx(stats, file = "02_output_plots_new/stats_conventional_a5_Pull_+50.xlsx")
```

## Quantiles of Sensitivity Results (anticipation = 10)

```{r, message = FALSE}
for (r in c("Europe", "North America", "Global")){
  
  stats <- data.results %>% 
  filter(region == r,
         anticipation == 10) %>% 
  select(!demand) %>% 
  unnest(sensitivities) %>% 
  unnest(results) %>% 
  filter(year %in% c(2025, 2030, 2050)) %>% 
  group_by(year) %>% 
  summarise(quibble(forecast))
  
  print(stats)
}

#write.xlsx(stats, file = "02_output_plots_new/stats_conventional_a10_Pull_+50.xlsx")
```

## Quantiles of Sensitivity Results (anticipation = 100)

```{r, message = FALSE}
for (r in c("Europe", "North America", "Global")){
  
  stats <- data.results %>% 
  filter(region == r,
         anticipation == 100) %>% 
  select(!demand) %>% 
  unnest(sensitivities) %>% 
  unnest(results) %>% 
  filter(year %in% c(2025, 2030, 2050)) %>% 
  group_by(year) %>% 
  summarise(quibble(forecast))
  
  print(stats)
}

#write.xlsx(stats, file = "02_output_plots_new/stats_conventional_a100_Pull_+50.xlsx")
```


## FIGURE 8: Unconventional growth sensitivity analysis of anticipation

```{r}
p1 <- plotProbabilisticFeasibilitySpace(
  data.row = data.results.unconv %>%
    filter(region == "Europe", anticipation == 0),
  data.targets = data.targets,
  colour = colours[2],
  marginal.year = 2038,
  title = "Europe, no anticipation",
  zoom.panel = F
)

p2 <- plotProbabilisticFeasibilitySpace(
  data.row = data.results.unconv %>%
    filter(region == "North America", anticipation == 0),
  data.targets = data.targets,
  colour = colours[2],
  marginal.year = 2038,
  title = "North America, no anticipation",
  zoom.panel = F
)

p3 <- plotProbabilisticFeasibilitySpace(
  data.row = data.results.unconv %>%
    filter(region == "Global", anticipation == 0),
  data.targets = data.targets,
  colour = colours[2],
  marginal.year = 2045,
  title = "Global, no anticipation",
  zoom.panel = F
)

p4 <- plotProbabilisticFeasibilitySpace(
  data.row = data.results.unconv %>%
    filter(region == "Europe", anticipation == 10),
  data.targets = data.targets,
  colour = colours[2],
  marginal.year = 2038,
  title = "Europe, 10 years anticipation",
  zoom.panel = F
)

p5 <- plotProbabilisticFeasibilitySpace(
  data.row = data.results.unconv %>%
    filter(region == "North America", anticipation == 10),
  data.targets = data.targets,
  colour = colours[2],
  marginal.year = 2038,
  title = "North America, 10 years anticipation",
  zoom.panel = F
)

p6 <- plotProbabilisticFeasibilitySpace(
  data.row = data.results.unconv %>%
    filter(region == "Global", anticipation == 10),
  data.targets = data.targets,
  colour = colours[2],
  marginal.year = 2045,
  title = "Global, 10 years anticipation",
  zoom.panel = F
)

p7 <- plotProbabilisticFeasibilitySpace(
  data.row = data.results.unconv %>%
    filter(region == "Europe", anticipation == 100),
  data.targets = data.targets,
  colour = colours[2],
  marginal.year = 2038,
  title = "Europe, full anticipation",
  zoom.panel = F
)

p8 <- plotProbabilisticFeasibilitySpace(
  data.row = data.results.unconv %>%
    filter(region == "North America", anticipation == 100),
  data.targets = data.targets,
  colour = colours[2],
  marginal.year = 2038,
  title = "North America, full anticipation",
  zoom.panel = F
)

p9 <- plotProbabilisticFeasibilitySpace(
  data.row = data.results.unconv %>%
    filter(region == "Global", anticipation == 100),
  data.targets = data.targets,
  colour = colours[2],
  marginal.year = 2045,
  title = "Global, full anticipation",
  zoom.panel = F
)

p.legend <- p1[[2]]

p.plots <- plot_grid(p1[[1]], p2[[1]],p3[[1]],
                     p4[[1]], p5[[1]],p6[[1]],
                     p7[[1]], p8[[1]],p9[[1]],
                     ncol = 3,
                     rel_widths = c(1, 1),
                     labels = "auto",
                     label_size = font.size)

p <- plot_grid(p.plots,
               NULL,
               p.legend,
               ncol = 3,
               rel_widths = c(1, 0.05, 0.15))

print(p)
ggsave(paste0(path.output, "FIG08_Sensitivity_Anticipation_Unconventional_Pull_+50.jpg"),
       width = 18, height = 18, units = "cm", bg = "white")
```

## Quantiles of Sensitivity Results (anticipation = 5)

```{r, message = FALSE}
for (r in c("Europe", "North America", "Global")){
  
  stats <- data.results.unconv %>% 
  filter(region == r,
         anticipation == 5) %>% 
  select(!demand) %>% 
  unnest(sensitivities) %>% 
  unnest(results) %>% 
  filter(year %in% c(2025, 2030, 2050)) %>% 
  group_by(year) %>% 
  summarise(quibble(forecast))
  
  print(stats)
}

#write.xlsx(stats, file = "02_output_plots_new/stats_unconventional_a5_Pull_+50.xlsx")
```

## Quantiles of Sensitivity Results (anticipation = 10)

```{r, message = FALSE}
for (r in c("Europe", "North America", "Global")){
  
  stats <- data.results.unconv %>% 
  filter(region == r,
         anticipation == 10) %>% 
  select(!demand) %>% 
  unnest(sensitivities) %>% 
  unnest(results) %>% 
  filter(year %in% c(2025, 2030, 2050)) %>% 
  group_by(year) %>% 
  summarise(quibble(forecast))
  
  print(stats)
}

#write.xlsx(stats, file = "02_output_plots_new/stats_unconventional_a10_Pull_+50.xlsx")
```

## Quantiles of Sensitivity Results (anticipation = 100)

```{r, message = FALSE}
for (r in c("Europe", "North America", "Global")){
  
  stats <- data.results.unconv %>% 
  filter(region == r,
         anticipation == 100) %>% 
  select(!demand) %>% 
  unnest(sensitivities) %>% 
  unnest(results) %>% 
  filter(year %in% c(2025, 2030, 2050)) %>% 
  group_by(year) %>% 
  summarise(quibble(forecast))
  
  print(stats)
}

#write.xlsx(stats, file = "02_output_plots_new/stats_unconventional_a100_Pull_+50.xlsx")
```


## FIGURE 9: Conservative growth sensitivity analysis of anticipation

```{r}
p1 <- plotProbabilisticFeasibilitySpace(
  data.row = data.results.conserv %>%
    filter(region == "Europe", anticipation == 0),
  data.targets = data.targets,
  colour = colours[3],
  marginal.year = 2038,
  title = "Europe, no anticipation",
  zoom.panel = F
)

p2 <- plotProbabilisticFeasibilitySpace(
  data.row = data.results.conserv %>%
    filter(region == "North America", anticipation == 0),
  data.targets = data.targets,
  colour = colours[3],
  marginal.year = 2038,
  title = "North America, no anticipation",
  zoom.panel = F
)

p3 <- plotProbabilisticFeasibilitySpace(
  data.row = data.results.conserv %>%
    filter(region == "Global", anticipation == 0),
  data.targets = data.targets,
  colour = colours[3],
  marginal.year = 2045,
  title = "Global, no anticipation",
  zoom.panel = F
)

p4 <- plotProbabilisticFeasibilitySpace(
  data.row = data.results.conserv %>%
    filter(region == "Europe", anticipation == 10),
  data.targets = data.targets,
  colour = colours[3],
  marginal.year = 2038,
  title = "Europe, 10 years anticipation",
  zoom.panel = F
)

p5 <- plotProbabilisticFeasibilitySpace(
  data.row = data.results.conserv %>%
    filter(region == "North America", anticipation == 10),
  data.targets = data.targets,
  colour = colours[3],
  marginal.year = 2038,
  title = "North America, 10 years anticipation",
  zoom.panel = F
)

p6 <- plotProbabilisticFeasibilitySpace(
  data.row = data.results.conserv %>%
    filter(region == "Global", anticipation == 10),
  data.targets = data.targets,
  colour = colours[3],
  marginal.year = 2045,
  title = "Global, 10 years anticipation",
  zoom.panel = F
)

p7 <- plotProbabilisticFeasibilitySpace(
  data.row = data.results.conserv %>%
    filter(region == "Europe", anticipation == 100),
  data.targets = data.targets,
  colour = colours[3],
  marginal.year = 2038,
  title = "Europe, full anticipation",
  zoom.panel = F
)

p8 <- plotProbabilisticFeasibilitySpace(
  data.row = data.results.conserv %>%
    filter(region == "North America", anticipation == 100),
  data.targets = data.targets,
  colour = colours[3],
  marginal.year = 2038,
  title = "North America, full anticipation",
  zoom.panel = F
)

p9 <- plotProbabilisticFeasibilitySpace(
  data.row = data.results.conserv %>%
    filter(region == "Global", anticipation == 100),
  data.targets = data.targets,
  colour = colours[3],
  marginal.year = 2045,
  title = "Global, full anticipation",
  zoom.panel = F
)

p.legend <- p1[[2]]

p.plots <- plot_grid(p1[[1]], p2[[1]],p3[[1]],
                     p4[[1]], p5[[1]],p6[[1]],
                     p7[[1]], p8[[1]],p9[[1]],
                     ncol = 3,
                     rel_widths = c(1, 1),
                     labels = "auto",
                     label_size = font.size)

p <- plot_grid(p.plots,
               NULL,
               p.legend,
               ncol = 3,
               rel_widths = c(1, 0.05, 0.15))

print(p)
ggsave(paste0(path.output, "FIG09_Sensitivity_Anticipation_Conservative_Pull_+50.jpg"),
       width = 18, height = 18, units = "cm", bg = "white")
```

## Quantiles of Sensitivity Results (anticipation = 5)

```{r, message = FALSE}
for (r in c("Europe", "North America", "Global")){
  
  stats <- data.results.conserv %>% 
  filter(region == r,
         anticipation == 5) %>% 
  select(!demand) %>% 
  unnest(sensitivities) %>% 
  unnest(results) %>% 
  filter(year %in% c(2025, 2030, 2050)) %>% 
  group_by(year) %>% 
  summarise(quibble(forecast))
  
  print(stats)
}

#write.xlsx(stats, file = "02_output_plots_new/stats_conservative_a5_PushBack_+50.xlsx")
```

## Quantiles of Sensitivity Results (anticipation = 10)

```{r, message = FALSE}
for (r in c("Europe", "North America", "Global")){
  
  stats <- data.results.conserv %>% 
  filter(region == r,
         anticipation == 10) %>% 
  select(!demand) %>% 
  unnest(sensitivities) %>% 
  unnest(results) %>% 
  filter(year %in% c(2025, 2030, 2050)) %>% 
  group_by(year) %>% 
  summarise(quibble(forecast))
  
  print(stats)
}

#write.xlsx(stats, file = "02_output_plots_new/stats_conservative_a10_PushBack_+50.xlsx")
```


## Quantiles of Sensitivity Results (anticipation = 100)

```{r, message = FALSE}
for (r in c("Europe", "North America", "Global")){
  
  stats <- data.results.conserv %>% 
  filter(region == r,
         anticipation == 100) %>% 
  select(!demand) %>% 
  unnest(sensitivities) %>% 
  unnest(results) %>% 
  filter(year %in% c(2025, 2030, 2050)) %>% 
  group_by(year) %>% 
  summarise(quibble(forecast))
  
  print(stats)
}

#write.xlsx(stats, file = "02_output_plots_new/stats_conservative_a100_PushBack_+50.xlsx")
``